\sf Retraction-based first-order feasible methods for difference-of-convex programs with smooth inequality and simple geometric constraints

### 2022-04-20 response_to_referee_v1.tex

	\textbf{Response:} Thanks for the comment. In fact,
\begin{equation*}
\begin{aligned}
\sigma^2 &= \|A(\widehat x_{\rm spgl1} + \tau(A^\dagger b - \widehat x_{\rm spgl1})) - b\|^2\\
 &=\tau^2\|A(A^\dagger b - \widehat x_{\rm spgl1})\|^2 + 2\tau\|A(A^\dagger b - \widehat x_{\rm spgl1})\|\|A(\widehat x_{\rm spgl1} - b\| + \|A(\widehat x_{\rm spgl1} - b\|^2
\end{aligned}
\end{equation*}
which is a quadratic function in $\tau$. It is easy to calculate $\tau$.

	\item  \textit{\textbf{Reviewer:}} \textit{Numerical results: As far as I see, Algorithm 3 does not require to find a completely feasible initial point ($x_0\in F$) but just in C ($x_0\in C$). I did not find any statement about how the initial point is chosen for ESQM$_{\rm ls}$. In principle, SPGL1 and Slater point are not needed. Therefore, it is not fair to say that FPA is faster since the sum of the iteration time plus the required initialization exceeds the CPU time of ESQM$_{\rm ls}$. Would it be any other cheaper way to compute $x_0$?}

	\textbf{Response:} Thanks for the comment. We choose different initial point for comparison in problem (6.1). When the initial point
$x^0 = (0, 0, \cdots, 0)$, we have the results in Table 1; When the initial point $x^0$ is given as in (6.6), we have the results in Table 2. Since the problem is non-convex, we can see from the results that the initial value has great influence on the efficiency of the algorithms. Although ESQM$_{\rm ls}$ is faster than FPA$_{\rm retract}$ when the initial value is zero, FPA$_{\rm retract}$ is faster than ESQM$_{\rm ls}$ when the initial point $x^0$ is given as in (6.6).

\begin{table}[H]
\caption{Computational results for problem (6.1) with initial point $x^0 = (0, 0, \cdots, 0)$}\label{table1}
\begin{center}
{\footnotesize
\begin{tabular}{|c|c|c|c|c|c|c|}\hline
\phantom{\diagbox{Date}{$i$}} & \multicolumn{1}{|c|}{Method} & \multicolumn{1}{|c|}{$i = 2$} & \multicolumn{1}{c|}{ $i = 4$ } & \multicolumn{1}{c|}{ $i = 6$ } & \multicolumn{1}{|c|}{ $i = 8$ } & \multicolumn{1}{c|}{ $i = 10$ }\\\cline{1-7}
\multirow{7}*{CPU time} & \multirow{1}*{QR}
&   0.50 &   3.11 &   9.79 &  22.95 &  43.99\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{Slater}
&   0.01 &   0.02 &   0.05 &   0.09 &   0.15\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{SPGL1}
&   1.38 &   7.54 &  15.69 &  28.50 &  50.25\\\cline{2-7} \multirow{1}*{} & \multirow{1}*{FPA$_{\rm retract}$}
&  14.09 &  62.33 & 139.27 & 241.40 & 388.70\\\cline{2-2} \multirow{1}*{}  & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.5}$}
&   4.92 &  25.75 &  59.09 & 102.56 & 170.23\\\cline{2-2} \multirow{1}*{}  & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.1}$}
&   4.42 &  21.80 &  49.89 &  86.37 & 142.02\\\cline{2-2} \multirow{1}*{}  & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.02}$}
&  13.36 &  59.88 & 135.25 & 236.76 & 378.49\\\cline{1-7} \multirow{4}*{Iter} & \multirow{1}*{FPA$_{\rm retract}$}
&   1638 &   1847 &   1885 &   1883 &   1957\\\cline{2-2} \multirow{1}*{}     & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.5}$}
&    759 &   1025 &   1075 &   1080 &   1158\\\cline{2-2} \multirow{1}*{}     & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.1}$}
&    767 &    913 &    946 &    941 &    991\\\cline{2-2} \multirow{1}*{}     & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.02}$}
&   2439 &   2579 &   2618 &   2620 &   2670\\\cline{1-7} \multirow{5}*{RecErr} & \multirow{1}*{SPGL1}
&  0.060 &  0.051 &  0.055 &  0.055 &  0.046\\\cline{2-7} \multirow{1}*{} & \multirow{1}*{FPA$_{\rm retract}$}
&  0.030 &  0.034 &  0.035 &  0.034 &  0.036\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.5}$}
&  0.030 &  0.034 &  0.035 &  0.034 &  0.036\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.1}$}
&  0.030 &  0.034 &  0.035 &  0.034 &  0.036\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.02}$}
&  0.030 &  0.034 &  0.035 &  0.034 &  0.036\\\cline{1-7} \multirow{5}*{Residual} & \multirow{1}*{SPGL1}
& -1.72e-04 & -2.10e-04 & -1.53e-04 & -1.37e-04 & -1.26e-04\\\cline{2-7} \multirow{1}*{} & \multirow{1}*{FPA$_{\rm retract}$}
& 1.69e-15 & 1.35e-15 & 2.79e-16 & -7.54e-16 & -1.42e-15\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.5}$}
& 1.21e-10 & 1.22e-10 & 1.12e-10 & 1.10e-10 & 1.11e-10\\\cline{2-2} \multirow{1}*{}      & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.1}$}
& 1.06e-10 & 9.98e-11 & 9.32e-11 & 9.36e-11 & 9.10e-11\\\cline{2-2} \multirow{1}*{}      & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.02}$}
& 1.01e-10 & 9.93e-11 & 9.77e-11 & 9.47e-11 & 9.60e-11\\\cline{1-7}
\end{tabular}
}
\end{center}
\end{table}

\begin{table}[H]
\caption{Computational results for problem (6.1) with initial point $x^0$ is given as in (6.6)}\label{table1}
\begin{center}
{\footnotesize
\begin{tabular}{|c|c|c|c|c|c|c|}\hline
\phantom{\diagbox{Date}{$i$}} & \multicolumn{1}{|c|}{Method} & \multicolumn{1}{|c|}{$i = 2$} & \multicolumn{1}{c|}{ $i = 4$ }
& \multicolumn{1}{c|}{ $i = 6$ } & \multicolumn{1}{|c|}{ $i = 8$ } & \multicolumn{1}{c|}{ $i = 10$ }\\\cline{1-7}
\multirow{7}*{CPU time} & \multirow{1}*{QR}
&   0.47 &   3.05 &   9.83 &  23.25 &  44.84\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{Slater}
&   0.01 &   0.02 &   0.05 &   0.09 &   0.15\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{SPGL1}
&   1.59 &   7.35 &  15.20 &  30.17 &  48.54\\\cline{2-7} \multirow{1}*{} & \multirow{1}*{FPA$_{\rm retract}$}
&   3.40 &  12.30 &  37.94 &  56.91 &  97.89\\\cline{2-2} \multirow{1}*{}  & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.5}$}
&   5.43 &  23.38 &  61.11 & 104.34 & 173.99\\\cline{2-2} \multirow{1}*{}  & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.1}$}
&   4.64 &  20.41 &  51.46 &  88.36 & 146.46\\\cline{2-2} \multirow{1}*{}  & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.02}$}
&  13.25 &  58.83 & 136.92 & 239.48 & 382.51\\\cline{1-7} \multirow{4}*{Iter} & \multirow{1}*{FPA$_{\rm retract}$}
&    420 &    368 &    520 &    444 &    493\\\cline{2-2} \multirow{1}*{}     & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.5}$}
&    893 &    937 &   1113 &   1099 &   1186\\\cline{2-2} \multirow{1}*{}     & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.1}$}
&    839 &    863 &    977 &    963 &   1025\\\cline{2-2} \multirow{1}*{}     & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.02}$}
&   2508 &   2550 &   2653 &   2650 &   2702\\\cline{1-7} \multirow{5}*{RecErr} & \multirow{1}*{SPGL1}
&  0.061 &  0.045 &  0.066 &  0.051 &  0.054\\\cline{2-7} \multirow{1}*{} & \multirow{1}*{FPA$_{\rm retract}$}
&  0.032 &  0.032 &  0.035 &  0.035 &  0.037\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.5}$}
&  0.032 &  0.032 &  0.035 &  0.035 &  0.037\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.1}$}
&  0.032 &  0.032 &  0.035 &  0.035 &  0.037\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.02}$}
&  0.032 &  0.032 &  0.035 &  0.035 &  0.037\\\cline{1-7} \multirow{5}*{Residual} & \multirow{1}*{SPGL1}
& -2.72e-04 & -2.20e-04 & -1.41e-04 & -1.19e-04 & -1.30e-04\\\cline{2-7} \multirow{1}*{} & \multirow{1}*{FPA$_{\rm retract}$}
& -1.86e-16 & 2.98e-16 & 1.85e-15 & -5.27e-16 & -1.31e-15\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.5}$}
& 1.08e-10 & 1.15e-10 & 1.01e-10 & 1.09e-10 & 1.05e-10\\\cline{2-2} \multirow{1}*{}      & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.1}$}
& 9.49e-11 & 9.50e-11 & 8.90e-11 & 9.60e-11 & 9.95e-11\\\cline{2-2} \multirow{1}*{}      & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.02}$}
& 9.35e-11 & 9.91e-11 & 9.14e-11 & 9.44e-11 & 9.34e-11\\\cline{1-7}
\end{tabular}
}
\end{center}
\end{table}

@@

	\item \textit{\textbf{Reviewer:}} \textit{ f) Subproblem (4.6): Should it be $\sigma^x$?}

    \textbf{Response:} Thanks for the comment. It should be $\sigma$ in subproblem (4.6). Indeed, in view of Lemma 4.1(iv), one can see that the inequality constraint in (4.6) is the same as
    \[
    \ell^{x^k}(Ax^k - b) + \langle A^T\nabla \ell^{x^k}(Ax^k - b),x-x^k\rangle \le \tilde \sigma^{x^k}.
    \]

	\item \textit{\textbf{Reviewer:}} \textit{ g) Please compare the algorithms with the method presented in [42], by the third author.}

    \textbf{Response:} Thanks for the comment. We compare the algorithms with SCP presented in [42] on solving problem (6.3):
    \begin{equation}\label{pr1}
       \begin{array}{rl}
        \min\limits_{x\in\R^n} & \|x\|_1 - \mu\|x\| \\\\
        {\rm s.t.} & \|Ax - b\|_{LL_2,\gamma}\leq \overline{\sigma},
       \end{array}
     \end{equation}
    Then, we have the results in Table 3.

\begin{table}[H]
\caption{Computational results for problem \eqref{pr1} with initial point $x^0$ is given as in (6.6)}\label{table3}
\begin{center}
{\footnotesize
\begin{tabular}{|c|c|c|c|c|c|c|}\hline
\phantom{\diagbox{Date}{$i$}} & \multicolumn{1}{|c|}{Method} & \multicolumn{1}{|c|}{$i = 2$} & \multicolumn{1}{c|}{ $i = 4$ }
& \multicolumn{1}{c|}{ $i = 6$ } & \multicolumn{1}{|c|}{ $i = 8$ } & \multicolumn{1}{c|}{ $i = 10$ }\\\cline{1-7}
\multirow{8}*{CPU time} & \multirow{1}*{QR}
&   0.56 &   3.17 &  10.04 &  23.39 &  45.84\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{Slater}
&   0.01 &   0.02 &   0.06 &   0.10 &   0.15\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{SPGL1}
&   3.24 &  13.12 &  34.00 & 205.99 & 233.59\\\cline{2-7} \multirow{1}*{} & \multirow{1}*{SCP}
&   2.67 &  14.19 &  19.85 &  39.25 &  58.30\\\cline{2-2} \multirow{1}*{}  & \multirow{1}*{FPA$_{\rm retract}$} 
&   4.57 & 191.87 &  40.39 & 128.89 & 160.03\\\cline{2-2} \multirow{1}*{}  & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.5}$}
&  17.38 &  66.68 & 123.05 & 211.69 & 179.34\\\cline{2-2} \multirow{1}*{}  & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.1}$}
&  16.54 &  65.41 & 137.92 & 217.52 & 294.88\\\cline{2-2} \multirow{1}*{}  & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.02}$}
&  18.35 &  82.69 & 195.55 & 329.15 & 397.47\\\cline{1-7} \multirow{5}*{Iter} & \multirow{1}*{SCP}
&    200 &    325 &    203 &    245 &    237\\\cline{2-2} \multirow{1}*{}     & \multirow{1}*{FPA$_{\rm retract}$} 
&    577 &   6069 &    567 &   1072 &    859\\\cline{2-2} \multirow{1}*{}     & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.5}$}
&   2590 &   2629 &   2204 &   2256 &   1236\\\cline{2-2} \multirow{1}*{}     & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.1}$}
&   2479 &   2578 &   2470 &   2315 &   2026\\\cline{2-2} \multirow{1}*{}     & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.02}$}
&   2766 &   3266 &   3505 &   3506 &   2741\\\cline{1-7} \multirow{6}*{RecErr} & \multirow{1}*{SPGL1}
&  1.699 &  3.423 &  1.826 &  2.630 &  2.465\\\cline{2-7} \multirow{1}*{} & \multirow{1}*{SCP}   
&  0.071 &  0.073 &  0.075 &  0.074 &  0.075\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{FPA$_{\rm retract}$}
&  0.071 &  0.073 &  0.075 &  0.074 &  0.075\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.5}$}
&  0.071 &  0.073 &  0.075 &  0.074 &  0.075\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.1}$}
&  0.071 &  0.073 &  0.075 &  0.074 &  0.075\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.02}$}
&  0.071 &  0.073 &  0.075 &  0.074 &  0.075\\\cline{1-7} \multirow{6}*{Residual} & \multirow{1}*{SPGL1}
& -5.45e-01 & -5.84e-01 & -7.09e-01 & -7.08e-01 & -7.38e-01\\\cline{2-7} \multirow{1}*{} & \multirow{1}*{SCP}
& -1.31e-10 & -1.53e-10 & -1.45e-10 & -1.78e-10 & -1.60e-10\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{FPA$_{\rm retract}$}
& -1.25e-12 & -1.37e-12 & -1.18e-12 & -1.22e-12 & -1.07e-12\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.5}$}
& 1.84e-11 & 1.94e-11 & 3.42e-11 & 4.38e-11 & 9.14e-11\\\cline{2-2} \multirow{1}*{}      & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.1}$}
& 2.62e-11 & 2.35e-11 & 2.58e-11 & 2.87e-11 & 2.32e-11\\\cline{2-2} \multirow{1}*{}      & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.02}$}
& 1.84e-11 & 1.52e-11 & 1.24e-11 & 1.41e-11 & 2.30e-11\\\cline{1-7}
\end{tabular}
}
\end{center}
\end{table}

### 2022-04-20 SQP+Retract_response_1.tex
Modified the second example

Before ending this section, we recall the following standard constraint qualifications on the constraint set of \eqref{P0} and the first-order necessary optimality conditions for \eqref{P0}.
\begin{definition}[{{\bf MFCQ}}]\label{MFCQ1}
We say that the Mangasarian-Fromovitz constraint qualifications for \eqref{P0} holds at an $x\in \mathcal{F}$ if the following implication holds:
\[
\left.\begin{matrix}
-\sum\limits_{i=1}^m\lambda_i \nabla g_i(x)\in \mathcal{N}_C(x)\\
\lambda_ig_i(x) =0, ~ i = 1, \ldots, m\\
\lambda_i\geq 0, ~ i = 1, \ldots, m
\end{matrix}\right\} \Rightarrow\lambda_i =0, ~ i = 1,\ldots, m.
\]
\end{definition}
Note that if the $g_i$'s in \eqref{P0} are in addition convex and the (generalized) Slater condition holds, i.e., $\{x \in C: g_i(x) < 0, ~ i = 1, \ldots, m\} \neq \emptyset $, then the MFCQ holds at any point in ${\cal F}$.
%Next, we recall the definition of stationary point of \eqref{P0} when $g$ is smooth.
\begin{definition}[{{\bf {\color{blue} Critical point}}}]\label{Stationary}
We say that $x\in\R^n$ is a {\color{blue}critical point} of \eqref{P0} if there exists $\lambda = (\lambda_1, \lambda_2, \ldots, \lambda_m)\in\R_+^m$ such that $(x,\lambda)$ satisfies
 \begin{enumerate}[{\rm (i)}]
   \item $g_i(x) \leq 0, ~ i = 1, \ldots, m$, and $x\in C$;
   \item $\lambda_ig_i(x)=0, ~ i = 1, \ldots, m$;
   \item $0\in\partial P_1(x) - \partial P_2(x) + \sum\limits_{i=1}^m\lambda_i \nabla g_i(x) + \mathcal{N}_C(x)$.
 \end{enumerate}
\end{definition}

@@

\subsection{Compressed sensing with Cauchy noise}\label{sec6.2}
In compressed sensing, when the measurement is contaminated with Cauchy noise, the Lorentzian norm $\|y\|_{LL_2,\gamma}:= \sum\limits_{i=1}^p\log(1 + \gamma^{-2}y_i^2)$ can be employed as the loss function \cite{CaBA10,CaRA16}, where $\gamma > 0$. In this section, we consider the following model for recovering sparse signal from measurements contaminated with Cauchy measurement noise, which uses an $\ell_{1-2}$-type regularizer as in \cite{YiLH15}:
\begin{equation}\label{E2}
  \begin{array}{rl}
\min\limits_{x\in\R^n} & \|x\|_1 - \mu\|x\|  \\
{\rm s.t.} & \|Ax - b\|_{LL_2,\gamma}\leq \overline{\sigma},
  \end{array}
\end{equation}
where $A\in\R^{p\times n}$ has full row rank, $b\in\R^p$, $\mu \in (0,1)$ and $\overline{\sigma} \in (0,\|b\|_{LL_2,\gamma})$. %Since $A$ has full row rank, there exists $\hx\in\R^n$ such that $A \hx = b$.

Although the feasible region of \eqref{E2} is unbounded and is not a special case of \eqref{P1}, one can argue as in the discussion following \eqref{E3} that \eqref{E2} is equivalent to the following model:
\begin{equation}\label{E4}
  \begin{array}{rl}
\min\limits_{x\in\R^n} & \|x\|_1 - \mu\|x\|  \\
{\rm s.t.} & \|Ax - b\|_{LL_2,\gamma}\leq \overline{\sigma},\\
           & \|x\|_{\infty} \leq M_1
  \end{array}
\end{equation}
as long as $M_1\ge \frac{\|A^\dagger b\|_1 - \mu\|A^\dagger b\|}{1 - \mu}$.
Notice that \eqref{E4} is a special case of \eqref{P1} with $P_1(x) = \|x\|_1$, $P_2(x) = \mu\|x\|$,  $\sigma=\overline{\sigma}$, $\ell(y) = \|y\|_{LL_2,\gamma}$, and $C = \{x\in\R^n:\; \|x\|_{\infty} \leq M_1\}$. One can see  from Example \ref{Loren} that Assumption~\ref{gassum} is satisfied for \eqref{E4}, and Assumption~\ref{assumption4} is satisfied for \eqref{E4} with $\xfeasss = A^\dagger b$. Hence, we can apply Algorithm \ref{SQP_retract2} to \eqref{E4}. In our numerical experiments below, we will be solving random instances of \eqref{E2} with $M_1 = \frac{\|A^\dagger b\|_1 - \mu\|A^\dagger b\|}{1 - \mu}$.

@@

\textbf{Initialization:} For \eqref{E3}, we first solve \eqref{E1} with $\mu = 0$ approximately using SPGL1 \cite{BeFr09} (version 2.1), under default settings, to obtain an approximate solution $x_{\rm spgl1}$. We then project $x_{\rm spgl1}$ onto the box $\{x:\; \max\limits_{J\in{\cal J}}\|x_J\|\le M\}$ to obtain $\widehat x_{\rm spgl1}$. The initial point $x^0$ is then generated as follows:
\begin{equation*}
x^0 = \begin{cases}
  \widehat x_{\rm spgl1} + \tau(A^\dagger b - \widehat x_{\rm spgl1}) & {\rm if}\ \|A\widehat x_{\rm spgl1} - b\| > \sigma,\\
  \widehat x_{\rm spgl1} & {\rm otherwise},
\end{cases}
\end{equation*}
where $\tau\in(0, 1)$ is a positive root of the quadratic equation $\|A(\widehat x_{\rm spgl1} + \tau(A^\dagger b - \widehat x_{\rm spgl1})) - b\|^2=\sigma^2$.
%In fact, since $\|A\xfeas - b\|^2 < \sigma^2$ and $\|Ax_{\rm spgl1} - b\|^2 > \sigma^2$, there must be exists $t\in[0, 1]$ such that $x = x_{\rm spgl1} + t(\xfeas - x_{\rm spgl1})$ with $\|Ax - b\|^2 = \sigma^2$.

>>>>

Before ending this section, we recall the following standard constraint qualifications on the constraint set of \eqref{P0} and the first-order necessary optimality conditions for \eqref{P0}.
\begin{definition}[{{\bf MFCQ}}]\label{MFCQ1}
We say that the Mangasarian-Fromovitz constraint qualifications for \eqref{P0} holds at an $x\in \mathcal{F}$ if the following implication holds:
\[
\left.\begin{matrix}
-\sum\limits_{i=1}^m\lambda_i \nabla g_i(x)\in \mathcal{N}_C(x)\\
\lambda_ig_i(x) =0, ~ i = 1, \ldots, m\\
\lambda_i\geq 0, ~ i = 1, \ldots, m
\end{matrix}\right\} \Rightarrow\lambda_i =0, ~ i = 1,\ldots, m.
\]
\end{definition}
Note that if the $g_i$'s in \eqref{P0} are in addition convex and the (generalized) Slater condition holds, i.e., $\{x \in C: g_i(x) < 0, ~ i = 1, \ldots, m\} \neq \emptyset $, {\color{blue} one can see from \cite[p341]{Ber95} that the MFCQ holds at any point in ${\cal F}$.}
%Next, we recall the definition of stationary point of \eqref{P0} when $g$ is smooth.
\begin{definition}[{{\bf {\color{blue} Critical point}}}]\label{Stationary}
We say that $x\in\R^n$ is a {\color{blue}critical point} of \eqref{P0} if there exists $\lambda = (\lambda_1, \lambda_2, \ldots, \lambda_m)\in\R_+^m$ such that $(x,\lambda)$ satisfies
 \begin{enumerate}[{\rm (i)}]
   \item $g_i(x) \leq 0, ~ i = 1, \ldots, m$, and $x\in C$;
   \item $\lambda_ig_i(x)=0, ~ i = 1, \ldots, m$;
   \item $0\in\partial P_1(x) - \partial P_2(x) + \sum\limits_{i=1}^m\lambda_i \nabla g_i(x) + \mathcal{N}_C(x)$.
 \end{enumerate}
\end{definition}

@@

\subsection{Compressed sensing with Cauchy noise in complex number}\label{sec6.2}
{\color{blue} In compressed sensing, when the measurement is contaminated with Cauchy noise, the Lorentzian norm $\|y\|_{LL_2,\gamma}:= \sum\limits_{i=1}^p\log(1 + \gamma^{-2}y_i^2)$ can be employed as the loss function \cite{CaBA10,CaRA16}, where $\gamma > 0$. In this section, we consider the following model for recovering sparse signal in complex number from measurements contaminated with Cauchy measurement noise, which motivated by the used of $\ell_{1-2}$-type regularizer in \cite{YiLH15}:
\begin{equation}\label{E2}
  \begin{array}{rl}
\min\limits_{x\in\R^n} & \sum\limits_{J\in\mathcal{J}}\|x_J\| - \mu\|x\| \\\\
{\rm s.t.} & \|Ax - b\|_{LL_2,\gamma}\leq \overline{\sigma},
  \end{array}
\end{equation}
where $A\in\R^{p\times n}$ has full row rank, $b\in\R^p$, $\mu \in (0,1)$ and $\overline{\sigma} \in (0,\|b\|_{LL_2,\gamma})$, $\mathcal{J}$ is a partition of $\{1,2,\cdots, n\}$, $x_J\in\R^{|J|}$ is the subvector of $x$ indexed by $J\in\mathcal{J}$.%Since $A$ has full row rank, there exists $\hx\in\R^n$ such that $A \hx = b$.

Although the feasible region of \eqref{E2} is unbounded and is not a special case of \eqref{P1}, one can argue as in the discussion following \eqref{E3} that \eqref{E2} is equivalent to the following model:
\begin{equation}\label{E4}
  \begin{array}{rl}
\min\limits_{x\in\R^n} & \sum\limits_{J\in\mathcal{J}}\|x_J\| - \mu\|x\| \\
{\rm s.t.} & \|Ax - b\|_{LL_2,\gamma}\leq \overline{\sigma},\\
           & \|x\|_{\infty} \leq M_1
  \end{array}
\end{equation}
as long as $M_1 \ge (1 - \mu)^{-1}[\sum\limits_{J\in\mathcal{J}}\|(A^\dagger b)_J\| - \mu\|A^\dagger b\|]$.
Notice that \eqref{E4} is a special case of \eqref{P1} with $P_1(x) = \sum\limits_{J\in\mathcal{J}}\|x_J\|$, $P_2(x) = \mu\|x\|$,  $\sigma=\overline{\sigma}$, $\ell(y) = \|y\|_{LL_2,\gamma}$, and $C = \{x\in\R^n:\; \|x\|_{\infty} \leq M_1\}$. One can see  from Example \ref{Loren} that Assumption~\ref{gassum} is satisfied for \eqref{E4}, and Assumption~\ref{assumption4} is satisfied for \eqref{E4} with $\xfeasss = A^\dagger b$. Hence, we can apply Algorithm \ref{SQP_retract2} to \eqref{E4}. In our numerical experiments below, we will be solving random instances of \eqref{E2} with $M_1 = (1 - \mu)^{-1}[\sum\limits_{J\in\mathcal{J}}\|(A^\dagger b)_J\| - \mu\|A^\dagger b\|]$. }

@@

\textbf{Initialization:} For \eqref{E3}, we first solve \eqref{E1} with $\mu = 0$ approximately using SPGL1 \cite{BeFr09} (version 2.1), under default settings, to obtain an approximate solution $x_{\rm spgl1}$. We then project $x_{\rm spgl1}$ onto the box $\{x:\; \max\limits_{J\in{\cal J}}\|x_J\|\le M\}$ to obtain $\widehat x_{\rm spgl1}$. The initial point $x^0$ is then generated as follows:
\begin{equation}\label{initial1}
x^0 = \begin{cases}
  \widehat x_{\rm spgl1} + \tau(A^\dagger b - \widehat x_{\rm spgl1}) & {\rm if}\ \|A\widehat x_{\rm spgl1} - b\| > \sigma,\\
  \widehat x_{\rm spgl1} & {\rm otherwise},
\end{cases}
\end{equation}
where $\tau\in(0, 1)$ is a positive root of the quadratic equation $\|A(\widehat x_{\rm spgl1} + \tau(A^\dagger b - \widehat x_{\rm spgl1})) - b\|^2=\sigma^2$.
%In fact, since $\|A\xfeas - b\|^2 < \sigma^2$ and $\|Ax_{\rm spgl1} - b\|^2 > \sigma^2$, there must be exists $t\in[0, 1]$ such that $x = x_{\rm spgl1} + t(\xfeas - x_{\rm spgl1})$ with $\|Ax - b\|^2 = \sigma^2$.

For \eqref{E4}, we first find a positive constant $\tau_0\in(0, 1)$ so that $\|b - A(\tau_0 A^\dagger b)\|_{LL_2,\gamma} = \overline\sigma$.\footnote{Note that $b - A(\tau_0 A^\dagger b) = (1 - \tau_0)b$, and hence such a $\tau_0$ can be found efficiently by first applying the Newton's method to obtain a root $s_*$ of the function $s\mapsto \|\sqrt{s}b\|_{LL_2,\gamma} - \overline\sigma$ (initialized at $s = 0$) and then setting $\tau_0 = 1 - \sqrt{s_*}$.}
Then we apply the SPGL1 \cite{BeFr09} (version 2.1) with default settings to approximately solve the following convex problem to obtain an approximate solution $x_{\rm spgl1}$:
\begin{equation}\label{SPGL1nonconvexL1}
\begin{array}{rl}
  \min\limits_{x\in \R^n} & \sum\limits_{J\in\mathcal{J}}\|x_J\| \\
  {\rm s.t.} & \ell^{\tau_0A^\dagger b}(Ax - b)\le \widetilde\sigma^{\tau_0A^\dagger b},
\end{array}
\end{equation}
where $\ell^{\tau_0A^\dagger b}$ and $\widetilde\sigma^{\tau_0A^\dagger b}$ are defined as in \eqref{defell} and \eqref{defsigma} respectively, with $\tau_0A^\dagger b$ in place of $y$ there. We then project $x_{\rm spgl1}$ onto the box $\{x:\; \|x\|_\infty\le M_1\}$ to obtain $\widetilde x_{\rm spgl1}$. The initial point $x^0$ is then generated as follows:
\begin{equation}\label{initial2}
x^0 = \begin{cases}
  \widetilde x_{\rm spgl1} + \tau_1(A^\dagger b - \widetilde x_{\rm spgl1}) & {\rm if}\ \|A\widetilde x_{\rm spgl1} - b\|_{LL_2,\gamma} > \overline\sigma,\\
  \widetilde x_{\rm spgl1} & {\rm otherwise},
\end{cases}
\end{equation}
where $\tau_1\in (0, 1)$ is chosen so that $\left\|b - A\left[\widetilde x_{\rm spgl1} + \tau_1(A^\dagger b - \widetilde x_{\rm spgl1})\right]\right\|_{LL_2,\gamma} = \overline\sigma$.\footnote{Note that $b - A[\widetilde x_{\rm spgl1} + \tau_1(A^\dagger b - \widetilde x_{\rm spgl1})] = (1 - \tau_1)(b-A \widetilde x_{\rm spgl1})$} One can find such a constant $\tau_1$ efficiently by first applying Newton's method to obtain a root $s_*$ of the function $s\mapsto \|\sqrt{s}(b - A\widetilde x_{\rm spgl1})\|_{LL_2,\gamma} - \overline\sigma$ (initialized at $s = 0$) and then setting $\tau_1 = 1 - \sqrt{s_*}$.
